Rust for Scientific Computing

### 2025-09-13 paper/main.tex
change title

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{Preprint}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{Rust for High-Performance Computing}

@@

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
    pdftitle={Rust for High-Performance Computing},
    pdfsubject={q-bio.NC, q-bio.QM},
    pdfauthor={Jonas Pleyer, Christian Fleck},
    pdfkeywords={},
}

>>>>

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{Preprint}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{Rust for Scientific Computing}

@@

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
    pdftitle={Rust for Scientific Computing},
    pdfsubject={q-bio.NC, q-bio.QM},
    pdfauthor={Jonas Pleyer, Christian Fleck},
    pdfkeywords={},
}
